A numerical study of variational data assimilation for the wave equation in heterogeneous media

### 2024-12-13 tex/main.tex
Updates from Overleaf

\noindent For $k \ge 1$, we define the $H^1$-conforming finite element space 
\begin{equation}
    V_h^k := \{ v \in H^1(\Omega) : v \vert_{K} \in \mathcal{P}^k(K) \ \forall K \in \mathcal{T}_h \},
\end{equation}
where $\mathcal{P}^k(K)$ denotes the space of polynomials of degree at most $k \in \mathbb{N}$ on $K \in \mathcal{T}_h$. Furthermore, we partition the time axis into $N$ subintervals $I_n = (t_n,t_{n+1})$, $n = 0, \dots, N-1$, where $0 = t_0 \le t_1 \le \dots \le t_N = T$. We assume that the intervals are of equal length and denote $\Delta t = \vert t_{n+1} -t_n \vert$. Then, we partition $Q$ and $\Sigma$ into time-slabs 
\begin{equation}
    \begin{aligned}
        Q^n := &I_n \times \Omega, \quad \Sigma^n := I_n \times \Sigma, \quad n = 0, \dots, N-1, \\
        Q = &\bigcup_{n = 0}^{N-1} Q^n, \quad \phantom{:} \Sigma = \bigcup_{n = 0}^{N-1} \Sigma^n.
    \end{aligned}
\end{equation}
In the following, we denote the space-time integrals on the time slabs as 
\begin{equation*}
    (u,v)_{Q^n} := \int_{I_n} \int_{\Omega} uv \ \dX \dT, \quad (u,v)_{\Sigma^n} := \int_{I_n} \int_{\Sigma} uv \ \dS \dT,
\end{equation*}
and define $\Vert v \Vert^2_{Q^n} := (v,v)_{Q^n}$ and $\Vert v \Vert^2_{\Sigma^n} := (v,v)_{\Sigma^n}$. 
Furthermore, we set 
\begin{equation*}
    \omega^n := I_n \times \omega, \quad (u,v)_{\omega^n} := \int_{I_n} \int_{\omega} uv \ \dX \dT, \quad \Vert v \Vert^2_{\omega_T} := \sum_{n = 0}^{N-1} (v,v)_{\omega^n}.
\end{equation*}
Finally, we define the time jump operator 
\begin{equation*}
    v^n_{\pm} (x) := \lim_{s \rightarrow 0^+} v(x,t_n \pm s), \quad \jump{v^n} := v^n_+ - v^n_-. 
\end{equation*}

@@

~\jp{I think that in the CIP we have to switch from the full gradient to the normal derivative  $\jump{c^2 \nabla \ul_1} \cdot \mathbf{n}$ only. Indeed, it follows from the first condition in \eqref{eq:IF-conditions} that the tangential part of the gradient on $\Gamma$ must be continuous $\jump{\nabla_{\Gamma} u} = 0$. So stabbilizing the full gradient is not consistent, which becomes an issue in Thm.~\ref{thm:bestapprox} as $S_h(\mathbf{U},\Wh) = 0$ would not hold.

>>>>

\noindent For $k \ge 1$, we define the $H^1$-conforming finite element space 
\begin{equation}
    V_h^k := \{ v \in H^1(\Omega) : v \vert_{K} \in \mathcal{P}^k(K) \ \forall K \in \mathcal{T}_h \},
\end{equation}
where $\mathcal{P}^k(K)$ denotes the space of polynomials of degree at most $k \in \mathbb{N}$ on $K \in \mathcal{T}_h$. Furthermore, we partition the time axis into $N$ subintervals $I_n = (t_n,t_{n+1})$, $n = 0, \dots, N-1$, where $0 = t_0 \le t_1 \le \dots \le t_N = T$. We assume that the intervals are of equal length and denote $\Delta t = \vert t_{n+1} -t_n \vert$. Then, we partition of $Q$ and $\Sigma$ into time-slabs 
\begin{equation}
    \begin{aligned}
        Q^n := &I_n \times \Omega, \quad \Sigma^n := I_n \times \Sigma, \quad n = 0, \dots, N-1, \\
        Q = &\bigcup_{n = 0}^{N-1} Q^n, \quad \phantom{:} \Sigma = \bigcup_{n = 0}^{N-1} \Sigma^n.
    \end{aligned}
\end{equation}
In the following, we denote the space-time integrals on the time slabs as 
\begin{equation*}
    (u,v)_{Q^n} := \int_{I_n} \int_{\Omega} uv \ \dX \dT, \quad (u,v)_{\Sigma^n} := \int_{I_n} \int_{\Sigma} uv \ \dS \dT,
\end{equation*}
and define $\Vert v \Vert^2_{Q^n} := (v,v)_{Q^n}$ and $\Vert v \Vert^2_{\Sigma^n} := (v,v)_{\Sigma^n}$. 
Furthermore, we set 
\begin{equation*}
    \omega^n := I_n \times \omega, \quad (u,v)_{\omega^n} := \int_{I_n} \int_{\omega} uv \ \dX \dT, \quad \Vert v \Vert^2_{\omega_T} := \sum_{n = 0}^{N-1} (v,v)_{\omega^n}.
\end{equation*}
Finally, we define the time jump operator 
\begin{equation*}
    v^n_{\pm} (x) := \lim_{s \rightarrow 0^+} v(x,t_n \pm s), \quad \jump{v^n} := v^n_+ - v^n_-. 
\end{equation*}

@@

~\jp{I think that in the CIP we have to switch from the full gradient to the normal derivative  $\jump{c^2 \nabla \ul_1} \cdot \mathbf{n}$ only. Indeed, it follows from the first conditon in \eqref{eq:IF-conditions} that the tangential part of the gradient on $\Gamma$ must be continuous $\jump{\nabla_{\Gamma} u} = 0$. So stabbilizing the full gradient is not consistent, which becomes an issue in Thm.~\ref{thm:bestapprox} as $S_h(\mathbf{U},\Wh) = 0$ would not hold.
